### 2023-01-19 paper.tex
Minor linguistic edits

	Source code repositories are an important aid to train systems that identify code smells and vulnerabilities. Code smells  are violations of fundamental design principles in the source code. Code smells can thus, apart from introducing errors in the code, also lead to suboptimal performance and efficiency. Code can further be optimized for maintainability, reusability, comprehensibility and extensibility~\cite{codesmellmining}. Apart from this, versions of the same source code can also provide an insight into the change of performance of the software over consecutive versions\cite{softwareversion}.

@@

	As already mentioned, consecutive versions of the same source code can help in detecting specific changes to the code performance due to specific changes in the source code ~\cite{softwareversion}. Whereas a comparison between disparate files requires establishment of a similarity measure at the beginning~\cite{simsimilarity}, earlier complete versions of the same source code can provide a benchmark on which to measure the performance of later versions ~\cite{softwareversion}. This can make it easier to detect optimizing patterns in the source code. These patterns, once established, can then be applied to optimizing similar inefficiencies in other source files. Hence, a repository containing multiple versions of each source file would prove to be helpful as a starting point in applying code mining approaches to optimizing smart contracts, which is a relatively unexplored research direction.

@@

	To the best of our knowledge, the analysis of smart contract code has only gained relatively little attention by the research community so far. Nevertheless, there are a number of according approaches for the optimization of gas cost of smart contracts, which we discuss in the following.

@@

	It can be argued that a database containing files originating only from public repositories of GitHub may not be representative of the currently deployed smart contracts. As mentioned before, multiple block explorers are available that list deployed smart contracts. However, most of these block explorers do not make the source code of the contracts is publicly accessible\todo{Something is wrong here in the sentence structure}, neither do they offer access to multiple versions of the same contract, a limitation which arises from the immutability of the blockchain. Under such circumstances, choosing GitHub as a foundation for the Smart Contract Repository is the logical choice since GitHub is the most popular among software development organizations, which makes it easier to assume that the code available on GitHub at least provides an estimation of deployed code. Similar approaches of using GitHub as a source of data for code mining algorithms can be found in literature\cite{schroder, dabic, yang}.\todo{Broken reference} However, usage of GitHub can lead to the inclusion of unfinished and untested source code in the repository, and as mentioned before, duplicate code, in the absence of a mechanism to properly handle forks.

@@

	\section{Analysis of the repository}
	In the previous section, it was mentioned that crawling GitHub might lead to distortions in the dataset. This section presents a short quantitative analysis of a sample of the database generated during experimentation. As written in Section~\ref{sec:implementation}, we were able to generate a corpus of 163,961 Solidity files, which were the results of 299,20437\todo{Something is wrong with this number} commits to Github.

@@

	As has already been mentioned before, the script, and consequently the repository, could be extended to include source files using other smart contract programming languages. Also, a compiler could be included as part of the script in order to generate and store the bytecode of the collected contracts. The source of data in the repository could be expanded, crawling other public repositories, or even private repositories a user may have access to. An attempt could be made to reconstruct the version history of a source file across multiple branches of the repository, to enable more fine-grained analysis. A gas-cost estimation framework, such as GASOL \cite{gasol} could be integrated into the script to generate gas cost estimations of the collected contract versions. Finally, the repository could be associated with a Web app that can make it easier to visualize the repository of contracts and also provide APIs for more nuanced filtering and retrieval of the dataset, even without knowledge of SQL. These tools could also be included as a plugin to an IDE that can enable easier interaction with the database.

>>>>

	Source code repositories are an important aid to train systems that identify code smells and vulnerabilities. Code smells  are violations of fundamental design principles in the source code. Code smells can thus, apart from introducing errors in the code, also lead to suboptimal performance and efficiency. Code can further be optimized for maintainability, reusability, comprehensibility and extensibility~\cite{codesmellmining}. Apart from this, versions of the same source code can also provide an insight into the change of performance of the software over consecutive versions~\cite{softwareversion}.

@@

	Consecutive versions of the same source code can help in detecting specific changes to the code performance due to specific changes in the source code ~\cite{softwareversion}. Whereas a comparison between disparate files requires establishment of a similarity measure at the beginning~\cite{simsimilarity}, earlier complete versions of the same source code can provide a benchmark on which to measure the performance of later versions ~\cite{softwareversion}. This can make it easier to detect optimizing patterns in the source code. These patterns, once established, can then be applied to optimizing similar inefficiencies in other source files. Hence, a repository containing multiple versions of each source file would prove to be helpful as a starting point in applying code mining approaches to optimizing smart contracts, which is a relatively unexplored research direction.

@@

	%To the best of our knowledge, the analysis of smart contract code has only gained relatively little attention by the research community so far.

	There are a number of according approaches for the optimization of gas cost of smart contracts, which we discuss in the following.

@@

	It can be argued that a database containing files originating only from public repositories of GitHub may not be representative of the currently deployed smart contracts. Multiple block explorers are available that list deployed smart contracts. However, most of these block explorers do not make the source code of the contracts is publicly accessible\todo{Something is wrong here in the sentence structure}, neither do they offer access to multiple versions of the same contract, a limitation which arises from the immutability of the blockchain. Under such circumstances, choosing GitHub as a foundation for the Smart Contract Repository is the logical choice since GitHub is the most popular among software development organizations, which makes it easier to assume that the code available on GitHub at least provides an estimation of deployed code. Similar approaches of using GitHub as a source of data for code mining algorithms can be found in literature\cite{schroder, dabic, yang}.\todo{Broken reference} However, usage of GitHub can lead to the inclusion of unfinished and untested source code in the repository and duplicate code, in the absence of a mechanism to properly handle forks.

@@

	\section{Analysis of the repository}
	%In the previous section, it was mentioned that crawling GitHub might lead to distortions in the dataset. 
	This section presents a short quantitative analysis of a sample of the database generated during experimentation. As written in Section~\ref{sec:implementation}, we were able to generate a corpus of 163,961 Solidity files, which were the results of 299,20437\todo{Something is wrong with this number} commits to Github.

@@

The script, and consequently the repository, could be extended to include source files using other smart contract programming languages. Also, a compiler could be included as part of the script in order to generate and store the bytecode of the collected contracts. The source of data in the repository could be expanded, crawling other public repositories, or even private repositories a user may have access to. An attempt could be made to reconstruct the version history of a source file across multiple branches of the repository, to enable more fine-grained analysis. A gas-cost estimation framework, such as GASOL \cite{gasol} could be integrated into the script to generate gas cost estimations of the collected contract versions. Finally, the repository could be associated with a Web app that can make it easier to visualize the repository of contracts and also provide APIs for more nuanced filtering and retrieval of the dataset, even without knowledge of SQL. These tools could also be included as a plugin to an IDE that can enable easier interaction with the database.
